---
title: "Birthday Analyzer"
author: "Cherie Yu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(rvest)
library(xml2)
library(httr)
library(dplyr)
library(purrr)
```


The `BdayAnalyzer` package contains functions helps you find your birthday secrets

##`Get_Url` Function
The `Get_Url` function helps you find the url related to your birthday analyzer.

This function asks the user to input birth year, month and day. 
The function will return the website link on one birthday of this user's input.

```Get_Url(1993,11,15)```

```{r eval=FALSE}
library(BdayAnalyzer)
Get_Url(1993,11,15)
```

Then the function will return the url of the related birthday. And you can check your more birthday features with it later.


##`Horoscope` Function
The `Horscope` function helps you find the starsign, element, and birthstone of the birthday desired from birthday analyzer.

A user call the function by puts in birth year, month and day.


```Horoscope(1993,11,15)```

```{r eval=FALSE}
Horoscope(1993,11,15)
```
Then the function will return desired information of the birthday of the user input.

##`FFF` Function
The `FFF` function helps you find the 3 friends , 2 foes , and 3famous people of the birthday desired from birthday analyzer.

A user call the function by puts in birth year, month and day.


```FFF(1993,11,15)```

```{r eval=FALSE}
FFF(1993,11,15)
```


##`FNelement` `FNstone` `FNstarsign` `FNfamous` `FNfoes` `FNfriend` Function

If you are interested in seeing only element, stone, starsign or one of the relationship info, you can use the simpler function like `FNelement` `FNstone` `FNstarsign` `FNfamous` `FNfoes` `FNfriend`. However, the inputs would require the url you obtained from the `Get_Url` function.

```FNelement```
```{r,eval=FALSE}
FNelement("https://www.thehoroscope.co/birthday-analyser/1993-11-15-horoscope-and-zodiac-sign-meanings-16035.html")

```

##`sampledata` Function

Finally, if someone wants to do more analysis on many birthdays, he can refer to the  `sample data` codes we have in the packge. In a nutshell, he can set the begin and end year of desired birthday, and provide birhtay analysis for the frequency he desires and return a dataframe that shows all the data.

```sampledata("1993-11-15","1994-2-15","months")```

```{r eval=FALSE, warning= FALSE}
sampledata("1993-11-15","1994-2-15","months")
```